Analysis of split plot design using MCMCglmm

### 2017-08-01 test_analysis.Rmd
Add test analysis with lme4; clean up Analysis.Rmd file

---
title: "Analysis of split plot design using MCMCglmm"
output: github_document
---

@@

If you have not already looked at the
[01-Probability_distribution_checks](01-Probability_distribution_checks.md),
please see that first to understand why MCMCglmm was chosen for this analysis
due to the nature of the data.

The analyses are semi-automated. When this file is knit, it automatically loads the _ProjectTemplate_ package and calls the `load.project()` function. This loads the data, cleans and munges it creating the `AUDPS` data frame used for the analysis below. The scripts used to clean and munge the data are located in the [munge](./munge) folder and numbered in the sequential order in which they are run.

#### Interpreting these analyses

For a quick overview, see this thread on Stack Overflow that walks through the output of `summary.MCMCglmm`,
which is used below. [R: Making sense of the output of a MCMCglmm](http://stackoverflow.com/questions/20993643/r-making-sense-of-the-output-of-a-mcmcglmm)

The MCMCglmm documentation is more in-depth but should still be referenced.
```{r MCMCglmm, eval=FALSE}
library(MCMCglmm)
vignette("Overview")
vignette("CourseNotes")
```

I found this CrossValidated topic to be useful in interpreting the outputs from
MCMCglmm as it explains the interpretation of the effects. While it is about
output from a `lmer`, the output is read in the same way, [How to interpret 2-way and 3-way interaction in lmer?](https://stats.stackexchange.com/questions/87412/how-to-interpret-2-way-and-3-way-interaction-in-lmer#87415).

@@

#### MCMCglmm model fitting notes

Fitting the models with the default iterations resulted in some less than
acceptable models. Because of this, the number of iterations has been increased,
`nitt = 5e+05` and `burnin = 5000` and `thin = 100`. This results in much
smaller errors for random effects and better models.

@@

Use `set.seed()` for reproducibility.

```{r set_seed}
set.seed(27)
```

@@

```{r 2015_TShB_incidence}
eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE,
                                    random = ~REP, 
                          data = AUDPS_2015,
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

summary(TShB_incidence_lmm_2015)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:10)])
reps <- melt(reps)

trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_incidence_lmm_2015$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Incidence")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Incidence")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Incidence")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Posteriors for Treatments, Tiller ShB Incidence")

# check random effects
plotTrace(TShB_incidence_lmm_2015$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_incidence_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Random Error Distribution for Tiller ShB Incidence"))
```

>>>>

---
  title: "Analysis of split plot design using lme4"
output: github_document
---

@@

@@

@@

@@

```{r 2015_TShB_incidence}
library(pbkrtest)
lmodr <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
lmoda <- lmer(TShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)

KRmodcomp(lmodr, lmoda)

lmodi <- lmer(yield ~ irrigation + (1|field),data=irrigation)
KRmodcomp(lmoda, lmodi)

lmodv <- lmer(yield ~  variety + (1|field),data=irrigation)
KRmodcomp(lmoda, lmodv)
```
